Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
LR subsection intro added

\caption{Permission-based conditions}
\label{fig:perm-conds}
\end{figure}
\clearpage
}
\todo[inline]{Add section introduction}

>>>>

\caption{Permission-based conditions}
\label{fig:perm-conds}
\end{figure}
\clearpage
}
%subsection introduction
The logical relation defines semantically what it means to be
capability safe. In large parts, capability safety is defined by
when a capability safely can be given to an untrusted piece of
code. In the following paragraphs, we will go through the definitions
of the logical relation and provide an intuition why they define
capability safety.
The definition of the logical relation is found in
\figurename~\ref{fig:logrel}, \figurename~\ref{fig:standard-regions},
and \figurename~\ref{fig:perm-conds}.
